---
title: "Assignment 1"
author: "PLSC 21510/31510"
date: "Fall 2022"
output: pdf_document
---

## Assignment 1 Solutions

- __Assigned__: 29 Sep 2022
- __Due__: 6 October 2022

**Instructions**: 
First read this [chapter](https://plsc-31101.github.io/course/strings-and-regular-expressions.html). 

Then answer the questions below. Knit this `.Rmd` document as a pdf and submit the pdf file in Canvas.

Please avoid printing long outputs (like entire dataframes). Your final pdf should be no more than 5 pages.

```{r message = FALSE}
library(tidyverse)
library(stringr)
```

## 1. Strings

#### 1.1

In your own words, describe the difference between the `sep` and `collapse` arguments to `str_c()`.


#### 1.2

Use `str_length()` and `str_sub()` to extract the middle character from 
a string. What will you do if the string has an even number of characters?

```{r}
# YOUR CODE HERE
```


#### 1.3

What does `str_trim()` do? What is the opposite of `str_trim()`?

- `str_trim()` removes whitespace from the start and the end of the string.
- `str_pad()` adds whitespace to the start and the end of the string.

#### 1.4

Split up a string like `"apples, pears, bananas"` into individual components.
      
```{r}
# YOUR CODE HERE
```

#### 1.5

What does splitting with an empty string (`""`) do? Experiment, and then read the documentation.
      
      
## 2. Regex

Use this vector of words:

```{r}
words <- stringr::words
```

Write code that prints the **number** of words that:

#### 2.1: Start with a vowel.

```{r}
# YOUR CODE HERE
```
  
#### 2.4: Start with a consonant. 

(Hint: Think about matching "not"-vowels.)
  
```{r}
# YOUR CODE HERE
```

#### 2.3: End with `ed`, but not with `eed`.
  
```{r}
# YOUR CODE HERE
```
      
#### 2.4: End with `ing` or `ise`.
  
```{r}
# YOUR CODE HERE
```

#### 2.5: Start or end with `x`.

```{r}
# YOUR CODE HERE
```

#### 2.6: Start with a vowel and end with a consonant.

```{r}
# YOUR CODE HERE
```

## 3. Applications

#### 3.1 

The file `transcripts.txt` contains a transcript of the Republican presidential primary debate hosted by Fox News at 9 p.m. on Aug. 6, 2015 in Cleveland, Ohio.

Using your `stringr` and regex skills, parse the file into a dataframe (`df`) with each row representing a "turn of talk." The dataframe should have two columns: 1) speaker, and 2) turn of talk. Remove applause lines. The file `transcript-parsed.csv` shows the final product.

```{r}
# Here's one way you can read a text file into R. 
library(readtext)
df <- readtext("transcript.txt")


# YOUR CODE HERE


# uncomment to test (`tibble` helps with pretty printing)
head(tibble(df))
```

## Bonus (Extra credit)

In class, we tried to find all sentences that contain a color.

```{r}
# create regex
colors <- c("red", "orange", "yellow", "green", "blue", "purple")
color_match <- str_c(colors, collapse = "|")

# Find sentences with colors
has_color <- str_subset(sentences, color_match)
head(has_color)

# Extract the color
matches <- str_extract(has_color, color_match)
head(matches)
```

We noticed that the regular expression matched words like "reared" and "shimmered", which are not colors color. Modify the regex to fix the problem.

```{r}
# YOUR CODE HERE
```